---
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: tango
---

```{r setup, include=FALSE}
# do not change this chunk
knitr::opts_chunk$set(echo=T, eval=T, fig.width=6, fig.height=4, warning=F, message=F )
```

# HW6 Answers
**PAF 573**

**YOUR NAME**

# Load libraries 
```{r, echo=T}
library(tidyverse)
library(jtools)
```

# Read in data 
```{r, echo=T}
# read in data 
URL <- "https://raw.githubusercontent.com/spiromar/files/main/paf573/greening.csv"
lots <- read.csv( URL )
```


# Problem 1  
Run a regression that estimates the difference in the mean number of vandalism calls in 2018 between the lots that were greened and those that were not. 

```{r}
# put regression here
```

What are some reasons why the difference you estimated might be biased upward? What are some reasons that it might be biased downward?  

**ANSWER:**

# Problem 2
Create a plot of the mean vandalism calls vs year, breaking out the means by whether or not the lot was in the greened group:
```{r}
ggplot(lots, aes(x=year, y=vcalls, group=greened, color=as.factor(greened))) + 
  stat_summary(fun = "mean", geom = "point") + 
  stat_summary(fun = "mean", geom = "line")
```

### 2.1  
What does this plot imply about which lots were selected for greening? What does it tell you about whether or not the greening had an effect on vandalism?

**ANSWER:**

### 2.2  
Estimate the effect of greening on vandalism by calculating a difference in difference estimate by hand. Use the year right before (2017) and the year right after the greening (2018).

**ANSWER:**  
```{r}
# use this space to get the data you need and do the calculation
```


# Problem 3
### 3.1  
Write down an equation for an interaction model that will give you the same information as in Q2.2. 

**ANSWER:**

### 3.2  
Estimate the model you wrote down in Q3.2. What is the differnce-in-differences estimate of the effect of greening on vandalism? Is it statistically significant? 

```{r}
# show work here

```

**ANSWER:**

### 3.3  
Interpret the other coefficients of the model, including the intercept.

**ANSWER:**

