---
output:
  html_document:
    theme: readable
    df_print: paged
    highlight: tango
---

```{r setup, include=FALSE}
# do not change this chunk
knitr::opts_chunk$set(echo=T, eval=T, fig.width=6, fig.height=4, warning=F, message=F )
```

# HW8 Answers
**PAF 573**

**YOUR NAME**  


# Question  
Include a one or two paragraph description of the question you are asking in your project

**ANSWER**  


# Data
Describe the data you are using.

Where did it come from? Include a link to a website if appropriate.

Is it longitudinal or cross-sectional?

What variable(s) are you using to measure your outcomes?

What variable(s) are your key regressors of interest?

**ANSWER**  
```{r}
# read in your data here and any additional libraries you need
# you can point to your own working directory. I don't need to be able 
# to read in the data myself. 
library(tidyverse)
library(jtools)

# show me the first 20 lines of your data for the important columns
# use something like this to do so:
# yourDatasetName %>% select(importantVariable1,importantVariable2, ...) %>% head(20)
```

# Sample Regression
Run a single regression using the an outcome variable and one key regressor. If you have any thoughts about where you are going beyond this with your analysis, please share and I will give you feedback. 

**ANSWER**  
```{r}

```

